Score-based tests of measurement invariance: Use in practice

### 2013-09-27 frontiers/frontiers.Rnw
update discussion part according to Ed's comment.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@269 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Because our sample size is large, this likelihood ratio test is known to be sensitive to 
small measurement invariance violations \cite{Ben80}.  That is, the above tests 
are sensitive to small measurement invariance violations that are not likely to be 
of interest to researchers.  For example, imagine that the 15-year-olds' 
parameters are slightly different than the other age groups.  
The 15-year-olds are in the middle of the age groups, and there 
is not likely to be any theoretical justification for 15-year-olds 
differing from every other age group.  One solution to this problem would be the {\em approximate invariance} methods proposed by Muth\'{e}n \cite{muthen13}\seeme{How to handle muthen's name in refs.bib file?}.
Alternatively, we can use the proposed family of score-based statistics to obtain tests that are sensitive to the ordering of age.

@@

\readme{First, summarize each step of the paper: In this paper, we first described a novel family of test statistics for measurement invariance and illustrated their use via the R package lavaan.  Next, we examined these statistics' ability to -.  We found -.}
In this paper, we examined the recently proposed ordinal statistics specificity property and robustness to model specification to study measurement invariance. As demonstrated in the results, the proposed statistics could select the modeled parameter violating measurement invariance even though the model is misspecified in general.

\readme{Now we need another short paragraph here describing what we will say in the sections below.}

@@

\subsection{Extension}
In this paper, We focused on testing for measurement invariance in factor analysis models that assume multivariate normality and that are estimated via ML.  The family of tests described here generally apply to estimation methods that maximize/minimize a fit function, however \cite<see>{zeihor07}, so they are potentially applicable to alternative SEM discrepancy functions such as Weighted Least Squares CITE.  Score calculation for these alternative discrepancy functions has not been implemented (to our knowledge), though the calculation certainly could be implemented.  Test statistic calculation and inference would then proceed in exactly the same manner as the calculation and inference illustrated in this paper.

>>>>

Because our sample size is large, this likelihood ratio test is known to be sensitive to 
small measurement invariance violations \cite{Ben80}.  That is, the above tests 
are sensitive to small measurement invariance violations that are not likely to be 
of interest to researchers.  For example, imagine that the 15-year-olds' 
parameters are slightly different than the other age groups.  
The 15-year-olds are in the middle of the age groups, and there 
is not likely to be any theoretical justification for 15-year-olds 
differing from every other age group.  One solution to this problem would be the {\em approximate invariance} methods proposed by Muth\'{e}n \cite{muthen13}.
Alternatively, we can use the proposed family of score-based statistics to obtain tests that are sensitive to the ordering of age.

@@

In this paper, we first described a novel family of test statistics for measurement invariance and illustrated their use via the R package lavaan. Next, we examined these statistics' ability to specifically pick up the violation parameter and specificity robustness to model specification. We found the proposed statistics could select the modeled parameter violating measurement invariance even though the model is misspecified in general.

In the reminder of the paper, we will first consider the applicability of these tests in exploring the reason of measurement invariance. Next, the extension of these tests to other fit functions and more specialized models will be discussed. 
\seeme{Are these two paragraphs OK?}

@@

\subsection{Extension}
In this paper, We focused on testing for measurement invariance in factor analysis models that assume multivariate normality and that are estimated via ML.  The family of tests described here generally apply to estimation methods that maximize/minimize a fit function, however \cite<see>{zeihor07}, so they are potentially applicable to alternative SEM discrepancy functions such as Weighted Least Squares \cite{bollen98}.  Score calculation for these alternative discrepancy functions has not been implemented (to our knowledge), though the calculation certainly could be implemented.  Test statistic calculation and inference would then proceed in exactly the same manner as the calculation and inference illustrated in this paper.
